---
title: "Section_1_Data_Cleaning_Script"
author: "Weige Yang, Zhu(Zoe) Yao, Shihan Wang, Ziyuan Yan"
date: "9/9/2019"
output: pdf_document
---

```{r}
#load packages.
library(dplyr)
library(tidyverse)
library(lfe)
library(stargazer)
```

Load randomized_data_for_hw.csv using read.csv.
```{r}
dat <- read.csv(file = '~/brandattitudes/randomized_data_for_hw.csv')
```

Log-transform ad metrics, competitor ad metrics, and brand attitude metrics using the log of (x+1).
```{r}
cols <- c("qua","val","sat","nat","loc","dig","compnat","comploc","compdig")
dat[cols] <- log1p(dat[cols])           
```

```{r}
Brand <- dat %>% pull(Brand)
Industry <- dat %>% pull(Industry)
time_period <- dat %>% pull(time_period)
yrqtr <- dat %>% pull(yrqtr)
qua_vol <- dat %>% pull(qua_vol)
```

Create 13 lag variables for each brand attitude metric.
```{r}
dat<- dat %>% 
  group_by(Brand) %>% 
  mutate(lag1qua = lag(qua, n=1),
         lag2qua = lag(qua, n=2), 
         lag3qua = lag(qua, n=3),
         lag4qua = lag(qua, n=4),
         lag5qua = lag(qua, n=5),
         lag6qua = lag(qua, n=6),
         lag7qua = lag(qua, n=7),
         lag8qua = lag(qua, n=8),
         lag9qua = lag(qua, n=9),
         lag10qua = lag(qua, n=10),
         lag11qua = lag(qua, n=11),
         lag12qua = lag(qua, n=12),
         lag13qua = lag(qua, n=13))

dat<- dat %>% 
  group_by(Brand) %>% 
  mutate(lag1val = lag(val, n=1),
         lag2val = lag(val, n=2), 
         lag3val = lag(val, n=3),
         lag4val = lag(val, n=4),
         lag5val = lag(val, n=5),
         lag6val = lag(val, n=6),
         lag7val = lag(val, n=7),
         lag8val = lag(val, n=8),
         lag9val = lag(val, n=9),
         lag10val = lag(val, n=10),
         lag11val = lag(val, n=11),
         lag12val = lag(val, n=12),
         lag13val = lag(val, n=13))

dat<- dat %>% 
  group_by(Brand) %>% 
  mutate(lag1sat = lag(sat, n=1),
         lag2sat = lag(sat, n=2), 
         lag3sat = lag(sat, n=3),
         lag4sat = lag(sat, n=4),
         lag5sat = lag(sat, n=5),
         lag6sat = lag(sat, n=6),
         lag7sat = lag(sat, n=7),
         lag8sat = lag(sat, n=8),
         lag9sat = lag(sat, n=9),
         lag10sat = lag(sat, n=10),
         lag11sat = lag(sat, n=11),
         lag12sat = lag(sat, n=12),
         lag13sat = lag(sat, n=13))
```

Create 5 lags for each advertising spend metric (both own brand and competitor).
```{r}
dat<- dat %>% 
  group_by(Brand) %>% 
  mutate(lag1nat = lag(nat, n=1),
         lag2nat = lag(nat, n=2), 
         lag3nat = lag(nat, n=3),
         lag4nat = lag(nat, n=4),
         lag5nat = lag(nat, n=5))

dat<- dat %>% 
  group_by(Brand) %>% 
  mutate(lag1loc = lag(loc, n=1),
         lag2loc = lag(loc, n=2), 
         lag3loc = lag(loc, n=3),
         lag4loc = lag(loc, n=4),
         lag5loc = lag(loc, n=5))

dat<- dat %>% 
  group_by(Brand) %>% 
  mutate(lag1dig = lag(dig, n=1),
         lag2dig = lag(dig, n=2), 
         lag3dig = lag(dig, n=3),
         lag4dig = lag(dig, n=4),
         lag5dig = lag(dig, n=5))

dat<- dat %>% 
  group_by(Brand) %>% 
  mutate(lag1compnat = lag(compnat, n=1),
         lag2compnat = lag(compnat, n=2), 
         lag3compnat = lag(compnat, n=3),
         lag4compnat = lag(compnat, n=4),
         lag5compnat = lag(compnat, n=5))

dat<- dat %>% 
  group_by(Brand) %>% 
  mutate(lag1comploc = lag(comploc, n=1),
         lag2comploc = lag(comploc, n=2), 
         lag3comploc = lag(comploc, n=3),
         lag4comploc = lag(comploc, n=4),
         lag5comploc = lag(comploc, n=5))

dat<- dat %>% 
  group_by(Brand) %>% 
  mutate(lag1compdig = lag(compdig, n=1),
         lag2compdig = lag(compdig, n=2), 
         lag3compdig = lag(compdig, n=3),
         lag4compdig = lag(compdig, n=4),
         lag5compdig = lag(compdig, n=5))
```

Drop the first 13 observations for each brand, since the lagged brand attitude metrics contain NAs during the first 13 weeks of the data.
```{r}
dat <- dat %>%
  group_by(Brand) %>%
  slice(14:n())
```
